---
title: "COHS French version validation"
author: "Lavinia Wuensch, Yoann Stussi, Théo Vernede, Eva R. Pool"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

# French validation of the Creature of Habit Scale

```{r setup, include=FALSE}
library(here)
library(ggplot2)
library(ggExtra)
library(jtools)
library(plyr)
library(dplyr)
library(tidyr)
library(psych)
library(devtools)
library(GPArotation)
library(nFactors)
library(RGenData)
library(lavaan)
library(data.table)
library(reshape2)
library(Hmisc)

# For network analysis
library(corrplot)
library(RColorBrewer)
library(bootnet)
library(networktools)
library(NetworkComparisonTest)
library(NetworkToolbox)
library(qgraph)

# devtools::install_github("hfgolino/EGAnet")
library(psychTools) 
library(EGAnet)

# For html tables
library(JWileymisc)
library(kableExtra)
library(knitr)

knitr::opts_chunk$set(echo = TRUE)

# Set up paths
data_path <- here::here("databases")
figures_path <- here::here("figures")
utilities_path <- here::here("analysis", "functions")

# Custom functions
source(file.path(utilities_path, "cpplus.r"))
source(file.path(utilities_path, "setup.r"))
```

## Describe the demographics of the population included in the COHS validation

```{r demographics, echo=TRUE, message= FALSE, warning= FALSE}
count.participants <- plyr::count(db.COHS.demo, c("sub"))

sum(count.participants$freq)

table_demo <- JWileymisc::egltable(c("Age", "Genre"), 
                      data = db.COHS.demo[c("Age","Genre")], strict = FALSE) %>%
  kbl(caption ="Demographics of sample used for the COHS validation", digits = 2)    %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_demo
```


## Check prerequirements

First we need to verify the postulates of covariance and have a look at the covariance plots. For the interpretation of the KMO: 

* 0.00 to 0.49 unacceptable.
* 0.50 to 0.59 miserable.
* 0.60 to 0.69 mediocre.
* 0.70 to 0.79 middling.
* 0.80 to 0.89 meritorious.
* 0.90 to 1.00 marvelous.

```{r cohs_validation_postulates_kmo,echo=TRUE, message=FALSE, warning=FALSE}
# Add formal tests for the variance covariance assumption
kmo.tab = KMO(db.COHS.cfa)

table_kmo <- knitr::kable(kmo.tab$MSAi, "html", caption = "Kmo Index", col.names = c("kmo")) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')
table_kmo

# Bartlett test
cor_matrix <- cor(db.COHS.cfa)
cortest.bartlett(cor_matrix, n = nrow(db.COHS.cfa))
```

## Descriptive values

Descriptive values of each item of the COHS:

```{r cohs_descritive,echo=TRUE, message= FALSE, warning= FALSE}
# Check distributions before proceeding with FA
a = psych::describe (db.COHS)

table_cohs_desc <- knitr::kable(a, "html", caption = "Descriptive values for each item of the COHS") %>%
  kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_cohs_desc
```

## Network analysis for the COHS

Run exploratory network analysis to identify communities:

```{r exploratory_network, echo=TRUE, message= FALSE, warning= FALSE}
cohs.ega <- EGAnet::EGA(db.COHS.cfa, model = "glasso", plot.EGA = F)

ega.figure <- plot(cohs.ega, 
                   node.color = c(pal[6], pal[9]),   
                   edge.color = c(pal[1], pal[10]),
                   legend.names = c("R", "A"),
                   edge.alpha = 0.1,
                   node.alpha = 0.7) 
ega.figure 

dev.print(pdf, file.path(figures_path, "cohs_validation_eganet.pdf"))
dev.off()
``` 

Display standardized loadings of each item to the two communities:

```{r loadings_network, echo=TRUE, message= FALSE, warning= FALSE}
net.loads(cohs.ega, loading.method = "original")$std
```

Run bootstrap EFA with the bootstrap of the EFA to extract the stability indices:

```{r cohs_run_bootstrap, echo=TRUE, message= FALSE, warning= FALSE}
cohs.boot <- EGAnet::bootEGA(db.COHS.cfa, model = "glasso", type = "parametric", iter = 1000, seed = 6724, plot.typical.ega = FALSE, plot.typicalStructure = FALSE)
```

Now we want to see how many times (out of 1 000) the two-factor solution was selected during bootstrapping:

```{r cohs_display_bootstrap, echo=TRUE, message= FALSE, warning= FALSE}
cohs.boot$frequency
```

Here we can see that the two-factor solution is chosen almost 80% of the time. Now we can try to have a look at the item stability (how many times one item was attributed to one factor during the bootstrap procedure).

```{r cohs_display_item_reliability, echo=TRUE, message= FALSE, warning= FALSE}
cohs.sc <- EGAnet::dimensionStability(cohs.boot, structure =cohs.ega$wc, IS.plot = F)

cohs.sc$item.stability$plot +
    ggplot2::scale_color_manual(values=c(pal[6], pal[9]), labels =c("R","A"))

dev.print(pdf, file.path(figures_path, "cohs_validation_egaboot.pdf"))
dev.off()
```

We can see that, overall, the item attribution is quite stable, with perhaps an exception with item 21 (though it is not terrible). 

```{r cohs_display_item_table,echo=TRUE, message= FALSE, warning= FALSE}
item.tab <- cohs.sc$item.stability$item.stability$all.dimensions

table_boot_item <- knitr::kable(item.tab, "html",caption = "Bootstrap procedure for the EGA dimensions") %>%
  kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_boot_item
```

What we can see is that item 21 often (12%) loads onto a third dimension (the number of structural dimensions of a network can be different than the number of factors, that is not a bug).

Let's have a look at the dimension stability:

```{r cohs_display_dimetion_consistency, echo=TRUE, message= FALSE, warning= FALSE}
cohs.sc$dimension.stability
```

## Correlation between Routine and Automaticity

Let's have a look at the correlation between the two expected subscales:

```{r cohs_correlation, echo=FALSE}
corrf = corr.test(db.COHS$COHS_automaticity, db.COHS$COHS_routine) 

print(corrf,short=FALSE)
```