---
title: "Rcode Habit components Experiment 2"
author: "Lavinia Wuensch, Yoann Stussi, Théo Vernade, Eva R Pool"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---



# R code for Experiment 2

```{r setup, echo=TRUE, message= FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

# load libraries necessary for the analyses
library(here)
library(car)
library(doBy)
library(ggplot2)
library(viridis)
library(ggExtra)
library(viridis)
library(jtools)
library(plyr)
library(dplyr)
library(tidyr)
library(psych)
library(devtools)
library(GPArotation)
library(nFactors)
library(RGenData)
library(data.table)
library(reshape2)
library(Hmisc)

# for network analysis
library(corrplot)
library(RColorBrewer)
library(bootnet)
library(networktools)
library(NetworkComparisonTest)
library(qgraph)

# libraries for htlm file 
library(JWileymisc)
library(kableExtra)
library(knitr)


```



```{r loaddata, include = FALSE}

#Set up path
data_path <- here::here("databases") # Source data path
figures_path <- here::here("figures")
utilities_path <- here::here("R")

source(file.path(utilities_path,'cpplus.r'))
source(file.path(utilities_path,'setup.r'))




```


## Population demographics

Total included participants:

```{r population, echo=TRUE}

count.participants <- plyr::count(Q2, c("sub"))
sum(count.participants$freq)

```

Gender and age:

```{r demo, echo=TRUE}

var.demo <- c('Age','Genre', 'FR')
db.demo <- Q2[var.demo]
db.demo$Genre <- factor (db.demo$Genre)
db.demo$FR <- factor (db.demo$FR)


table_demo_exp1 <- JWileymisc::egltable(c("Age", "Genre","FR"), 
                     data = db.demo[c("Age","Genre","FR")], strict = FALSE) %>%
  kbl(caption ="Demographics of sample used for Experiment 2", digits = 2)    %>%
  kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

 table_demo_exp1
 
 
 

```


## Descriptives analysis

Get the means, n and standard deviations of the questionnaires.


```{r descriptives_stats, echo=TRUE, message= FALSE, warning= FALSE}

# questionnaires totals
var.totals <- c("CESD_total",
                "COHS_total", 
                "EAT26_total",
                "EDSR_total",
                "GAS_total",
                "IAT_total",
                "LSAS_total",
                "OCIR_total",
                "PCLS_total",
                "PSS_total",
                "QABB_total",
                "SASSV_total",
                "STICSAT_total",
                "UPPS_total",
                "YFAS_score")

db.totals<- Q2[var.totals]
descr.exp2 = psych::describe(db.totals)

table_exp2_desc <- knitr::kable(descr.exp2, "html", caption = "Descriptive values for questionnaires of Experiment 2") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp2_desc



```


```{r alphas, echo=TRUE, message= FALSE, warning= FALSE}


my.scales <- scoreItems(Q2.alphas,Q2)
my.scales$alpha

```

## Plot of the distributions


```{r plot_distribution, echo=TRUE, message= FALSE, warning= FALSE}



var.plot <- c( "CESD_total",
               "COHS_total", 
               "EAT26_total",
               "IAT_total",
                "PSS_total",   
               "OCIR_total",   
               "UPPS_total",
               "STICSAT_total",
                "SASSV_total",
                "GAS_total",
                "EDSR_total",
                "PCLS_total",
                "LSAS_total",
                "YFAS_score", 
                "QABB_total",
                "id")

db.plot <- Q2[var.plot]

# now we need to have that in a long format because it's easy for the plots
db_long <- gather(db.plot, questionnaire , score, CESD_total:QABB_total, factor_key=TRUE)

# labels
labels <- c(EAT26_total = "EAT", 
            COHS_total = "COHS",
            PSS_total = "PSS",
            IAT_total = "IAT", 
            PCLS_total = "PCL-S", 
            OCIR_total = "OCI", 
            STICSAT_total = "STICSA",
            UPPS_total = "UPPS",
            SASSV_total ="SAS" ,
            GAS_total = "GAS",
            EDSR_total = "EDS-R",
            LSAS_total = "LSAS",
            YFAS_score = "YFAS",
            QABB_total = "QABB",
            CESD_total = "CES-D")

# let's plot distribution
pp = ggplot(data = db_long, aes (x = score, fill = questionnaire)) +
  facet_wrap(~questionnaire, scales = "free", labeller = labeller(questionnaire = labels) ) +
  geom_histogram(aes(y=..density..),alpha=0.6) +
  geom_density(aes(color = questionnaire), alpha = 0.3) +
  scale_fill_viridis_d(name = "Questionnaires", 
                       begin = .1, end = .9,
                       option = "inferno",
                       aesthetics = c("color", "fill"),
                       labels = labels)+
  theme_bw()+
  labs(
    title = '',
    x = 'Questionnaires',
    y = "Frequency"
  )

# let's make the plot nice looking
ppp <-   pp + theme_bw(base_size = 10, base_family = "Helvetica")+
  theme(strip.text.x = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(color="white", fill="white", linetype="solid"),
        axis.ticks.x = element_blank(),
        axis.text.x  = element_blank(),
        axis.title.x = element_text(size = 15, face = "bold"),
        axis.title.y = element_text(size = 15, face = "bold"),
        legend.position = "none")

ppp

# let's print the plot in a pdf document
pdf(file.path(figures_path,'Figure_Exp2_Questionnaires_distribution.pdf'))
print(ppp)
dev.off()

```

## Extract Factors from subscales

```{r efa_describe, echo=TRUE, message= FALSE, warning= FALSE}

# questionnaires subscales
var.subscales <- c("EAT26_dieting", 
                "EAT26_bulimia",
                "EAT26_oral_control",
                "YFAS_score",
                "STICSAT_traitsomatic",
                "STICSAT_traitcognitive",
                "LSAS_fear",
                "LSAS_avoidance",
                "PSS_total",
                "PCLS_intrusion",
                "PCLS_evitement",
                "PCLS_hyperstimulation",
                "COHS_routine", 
                "COHS_automaticity",
                "CESD_depressed",
                "CESD_positive",
                "CESD_somatic",
                "CESD_relationship",
                "EDSR_tolerance",
                "EDSR_withdrawal",
                "EDSR_lack_control",
                "EDSR_time",
                "EDSR_reduction_activities",
                "EDSR_intention",
                "EDSR_continuance",
                "BISBAS_BAS_Drive",
                "BISBAS_BAS_Fun",
                "BISBAS_BAS_Reward",
                "BISBAS_BIS", 
                "UPPS_negative_urgency",
                "UPPS_premeditation",
                "UPPS_positive_urgency",
                "UPPS_perseverance",
                "UPPS_sensation",
                "OCIR_checking",
                "OCIR_ordering",
                "OCIR_obsessing",
                "OCIR_hearding",
                "OCIR_washing",
                "OCIR_neutralising",
                "GAS_total", 
                "IAT_salience",
                "IAT_excessive_use",
                "IAT_neglect_work",
                "IAT_anticipation",
                "IAT_lack_control",
                "IAT_neglect_social_life",
                "SASSV_total",
                "QABB_total")

db.subscales <- Q2[var.subscales]

# remove  questionnaire
db.efa.exp2 <- subset(db.subscales, select = -c(COHS_routine,COHS_automaticity, 
                                           BISBAS_BAS_Drive,
                                           BISBAS_BAS_Fun,
                                           BISBAS_BAS_Reward,
                                           BISBAS_BAS_Drive,
                                           BISBAS_BIS,
                                           UPPS_negative_urgency,
                                           UPPS_positive_urgency,
                                           UPPS_perseverance,
                                           UPPS_premeditation,
                                           UPPS_sensation))



db.efa.descr2 = psych::describe(db.efa.exp2)


table_exp2_efa_descr <- knitr::kable(db.efa.descr2 , "html", caption = "Descriptive values for subscales used in Experiment 2") %>%
  kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp2_efa_descr 
```

Verify postulates with KMO and Bartlett test

```{r efa_postulates, echo=TRUE, message= FALSE, warning= FALSE}

KMO (db.efa.exp2)

cor_matrix <- cor(db.efa.exp2, use = "complete.obs")

cortest.bartlett(cor_matrix, n = nrow(db.efa.exp2))
```
The first method we use is the parallel analysis

```{r efa_fa.parallel, echo=TRUE, message= FALSE, warning= FALSE} 

nFact  <- fa.parallel(db.efa.exp2, fm = "ml") 
```
 Second method is VSS 
 
```{r efa_vss, echo=TRUE, message= FALSE, warning= FALSE} 
nFact <- vss(db.efa.exp2)
 
```


nScree method

```{r efa_nscreen, echo=TRUE, message= FALSE, warning= FALSE} 
nFact  <- nScree(x = na.omit(db.efa.exp2), model = "factors") 
plotnScree(nFact) 
```

Try method "comparison data"

```{r efa_compdata, echo=TRUE, message= FALSE, warning= FALSE} 
nFact <- EFACompData(na.omit(db.efa.exp2), 10, n.pop = 10000, n.samples = 500, alpha = .30, graph = T,corr.type = "pearson") 
```

# apply EFA with oblimin rotation

```{r efa_fa, echo=TRUE, message= FALSE, warning= FALSE} 

quest.sc.efa2 <- fa(r = db.efa.exp2, nfactors =6, rotate = "oblimin", fm = "ml") 
print(quest.sc.efa2$loadings,cutoff = 0.2)

```

## Compute factor scores 

 We compute factor scores but importantly we assess factor indeterminacy to control if the factor can be used as predictors 


```{r efa_loading, echo=TRUE} 

s.exp2 = factor.scores (db.efa.exp2, quest.sc.efa2) 
s.exp2$R2

```
 
## Plot correlation matrix of all subscales
 
 
```{r plot_correlation_matrix, echo=FALSE,warning=FALSE, message=FALSE}
 
 # rename variables
col_old = stringr::str_remove(var.subscales, "COHS_automaticity")
col_old = stringr::str_remove(col_old , "COHS_routine")
col_old = stringr::str_remove(col_old , "BISBAS_BAS_Reward")
col_old = stringr::str_remove(col_old , "BISBAS_BAS_Fun")
col_old = stringr::str_remove(col_old , "BISBAS_BAS_Drive")
col_old = stringr::str_remove(col_old , "BISBAS_BIS")
col_old = stringr::str_remove(col_old , "UPPS_premeditation")
col_old = stringr::str_remove(col_old , "UPPS_perseverance")
col_old = stringr::str_remove(col_old , "UPPS_sensation")
col_old = stringr::str_remove(col_old , "UPPS_positive_urgency")
col_old = stringr::str_remove(col_old , "UPPS_negative_urgency")

col_old = col_old[col_old != ""]
 
col_new <- c(   "EAT: dieting", 
                "EAT: bulimia",
                "EAT: oral contr.",
                "YFAS",
                "STICSA: som.",
                "STICSA: cogn.",
                "LSAS: fear",
                "LSAS: avoid.",
                "PSS",
                "PCLS: intr.",
                "PCLS: avoid.",
                "PCLS: hypersti.",
                "CESD: depr.",
                "CESD: pos.",
                "CESD: som.",
                "CESD: relation.",
                "EDS: toler.",
                "EDS: withdraw.",
                "EDS: lack contr.",
                "EDS: time",
                "EDS: red. act.",
                "EDS: intent.",
                "EDS: cont.",
                "OCI: check.",
                "OCI: order.",
                "OCI: obsess.",
                "OCI: heard.",
                "OCI: wash.",
                "OCI: neutr.",
                "GAS", 
                "IAT: salience",
                "IAT: exces. use",
                "IAT: negl. work",
                "IAT: anticip.",
                "IAT: lack contr.",
                "IAT: negl. social",
                "SASSV",
                "QABB")


colnames(db.efa.exp2)[colnames(db.efa.exp2) == col_old] <- col_new
corrmatrix <- cor(db.efa.exp2, use="complete.obs")
col1 <- colorRampPalette(brewer.pal(9,"BrBG"))
corrplot(corrmatrix,method = "square", tl.col = "black", tl.cex = 0.5, sig.level = 0.05, insig = "pch", pch.cex = 1, col = col1(100))
dev.print(pdf, file.path(figures_path,'Figure_Exp2_correlation_matrix.pdf'))
dev.off()
 
```
 
## Extract transdiagnostic Factors based on the EFA
 
 
```{r plot_factor_loadings,echo=TRUE, message= FALSE, warning= FALSE} 

 # get loadings into a dataset
load = quest.sc.efa2$loadings
load = load[]
load = data.frame(load)
setDT(load,keep.rownames=TRUE)[]
colnames(load)[1] <- "Subscale"



loadings.m <- melt(load, id=c("Subscale"),
                   measure=c("ML3","ML1","ML2","ML4","ML5","ML6"),
                   variable.name="Factor", value.name="Loading")

loadings.m$subscale <- c(   "EAT: dieting", 
                "EAT: bulimia",
                "EAT: oral contr.",
                "YFAS",
                "STICSA: som.",
                "STICSA: cogn.",
                "LSAS: fear",
                "LSAS: avoid.",
                "PSS",
                "PCLS: intr.",
                "PCLS: avoid.",
                "PCLS: hypersti.",
                "CESD: depr.",
                "CESD: pos.",
                "CESD: som.",
                "CESD: relation.",
                "EDS: toler.",
                "EDS: withdraw.",
                "EDS: lack contr.",
                "EDS: time",
                "EDS: red. act.",
                "EDS: intent.",
                "EDS: cont.",
                "OCI: check.",
                "OCI: order.",
                "OCI: obsess.",
                "OCI: heard.",
                "OCI: wash.",
                "OCI: neutr.",
                "GAS", 
                "IAT: salience",
                "IAT: exces. use",
                "IAT: negl. work",
                "IAT: anticip.",
                "IAT: lack contr.",
                "IAT: negl. social",
                "SASSV",
                "QABB") 

loadings.m$subscale <- factor(loadings.m$subscale, levels = loadings.m$subscale[seq (1:38)])


# name factors
labels <- c(ML3 = "Social Anx.", ML1 = "Stress",
            ML2 = "Exercise", ML5 = "Eating", 
            ML4 = "Media", 
            ML6 = "Comp.")

pp <- ggplot(loadings.m, aes(subscale, abs(Loading), fill=Loading)) +
  facet_wrap(~ Factor, nrow=1, labeller = labeller(Factor = labels) ) +
  geom_bar(stat="identity") + #make the bars
  coord_flip() + #flip the axes so the test names can be horizontal
  scale_fill_gradient2(name = "Loading",
                       high = "#006666", mid = "white", low = "goldenrod4",
                       midpoint=0, guide=F) +
  scale_x_discrete(limits = rev(levels(loadings.m$subscale)))+
  ylab("Loading Strength") +
  theme_bw(base_size=10)


# let's make the plot nice looking
ppp <-   pp + theme_bw(base_size = 10, base_family = "Helvetica")+
  theme(strip.text.x = element_text(size = 8, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(color="white", fill="white", linetype="solid"),
        axis.title.x = element_text(size = 15, face = "bold"),
        axis.title.y = element_text(size = 15, face = "bold"),
        legend.position = "none")

ppp

dev.print(pdf, file.path(figures_path,'Figure_Exp2_Factors.pdf'))
dev.off()

```
 
## Factors correlations

```{r factor_correlation, echo=TRUE, message= FALSE, warning= FALSE} 

var.net = c("COHS_automaticity", "COHS_routine", "UPPS_total" )
db.network.tmp2 <- Q2[var.net]

# merge with the FULL database
axes.exp2 <- s.exp2$scores

# combine
db.network.exp2 <- cbind(db.network.tmp2, axes.exp2)


# rename with interpreted factors
old_names = c ("COHS_automaticity", "COHS_routine","UPPS_total",
               "ML1","ML2","ML4",
               "ML6","ML5","ML3")

new_names <- c("Automaticity","Routine","Impuls.",
               "Stress","Exercise",
               "Media","Comp.","Eat",
               "Social Anx.")

colors <- c(pal[8], pal[8],pal[8],
            pal[9], pal[9], pal[9],
            pal[9], pal[9], pal[9],
            pal[9])



colnames(db.network.exp2)[colnames(db.network.exp2) == old_names] <- new_names

# descriptive correlation
factor_corr_plot <- cpplus(db.network.exp2, reorder=FALSE, alpha=0.05)


dev.print(pdf, file.path(figures_path,'Figure_Exp2_Factors_correlation.pdf'))
dev.off()


```
 
## Network Dynamic Analysis


Centrality Table
```{r network_centrality, echo=TRUE, message= FALSE, warning= FALSE} 
# estimate network
mynetwork.exp2 <- estimateNetwork(db.network.exp2, default ="EBICglasso") # lasso with ebic hyperparameter is 0.5

CentralityTable <- centralityTable(mynetwork.exp2)


EITable <- subset(CentralityTable, measure == "ExpectedInfluence")

table_exp2_ei <- knitr::kable(EITable , "html", caption = "Centrality Table Experiment 2") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp2_ei

```

```{r network_plot, echo=TRUE, message= FALSE, warning= FALSE} 
 
nledges <- getWmat(mynetwork.exp2)

plot_network.exp2 <- qgraph(nledges,
       layout = "spring",
       labels = new_names,
       label.scale = F,
       label.cex = 1,
       edge.labels = F,
       #cut = 0.1,
       color = colors,
       border.color = colors,
       border.width = 4,
       node.width = 0.9,
       posCol = c("#006666","#006666"),
       negCol = c("goldenrod4","goldenrod4"),
       vTrans = 150,
       label.font = 2
       )


dev.print(pdf, file.path(figures_path,'Figure_Exp2_Network.pdf'))
print(plot_network.exp2)
dev.off()
 
```


## Estimate the network stability


First for the edges that are what matters the most for our hypothesis

```{r network_stability_edges, echo=TRUE, message= FALSE, warning= FALSE} 

# set seed to obtain reproduceble results
set.seed(1331)
b1 <- bootnet(mynetwork.exp2, nBoots= 10000, nCores = 1,
              statistics = c("strength","expectedInfluence","edge"),caseN = 50)


tb.b1 = summary(b1)

table_exp2_boot <- knitr::kable(tb.b1 , "html", caption = "Table Experiment 2") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp2_boot

plot (b1, plot = "interval", split0 = TRUE, order="sample", labels=T)


```


and now for the centrality indexes 

```{r network_stability_centrality, echo=TRUE, message= FALSE, warning= FALSE} 

set.seed(1331)
b2 <- bootnet(mynetwork.exp2, nBoots= 10000, nCores = 1, type = "case",
              statistics = c("strength","expectedInfluence","edge"),caseN = 50)

corStability(b2)

plot (b2, c("expectedInfluence"))# centrality stability graph


```
 
 