---
title: "Differential influence of habit components on problematic behaviors - Revision 1"
author: "Lavinia Wuensch, Yoann Stussi, Théo Vernede, Eva R. Pool"
date: "`r format(Sys.time(), '%d %B, %Y')`"
format: 
  html:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
    embed-resources: true
---

# Setup

```{r}
#| label: "setup"
#| include: false
knitr::opts_chunk$set(echo = TRUE)

library(cowplot)
library(tidyverse)
library(ggpubr)

# Load libraries
library(here)
library(car)
library(afex)
library(doBy)
library(ggplot2)
library(viridis)
library(ggExtra)
library(viridis)
library(jtools)
library(plyr)
library(dplyr)
library(tidyr)
library(psych)
library(devtools)
library(GPArotation)
library(nFactors)
library(RGenData)
library(lavaan)
library(semPlot)
library(data.table)
library(reshape2)
library(Hmisc)

# For network analysis
library(corrplot)
library(RColorBrewer)
library(bootnet)
library(networktools)
library(NetworkComparisonTest)
library(qgraph)

# For html file 
library(JWileymisc)
library(kableExtra)
library(knitr)

# Set paths
here::i_am("analysis/revision_1.qmd")
data_path <- here::here("databases")
figures_path <- here::here("figures")
utilities_path <- here::here("analysis", "functions")
results_path <- here::here("results")

# Source
source(str_c(utilities_path, "/cpplus.r"))

# Set theme
html_theme <- theme_cowplot(font_family = "Helvetica")

# Select color palette
pal <- viridis::viridis(n = 10)
pal2 <- viridis::inferno(n = 10)
```

```{r}
#| label: "import_data"
#| include: false

experiment_1_factors <- readRDS(str_c(results_path, "/experiment_1_factors.rds"))
experiment_2_factors <- readRDS(str_c(results_path, "/experiment_2_factors.rds"))
```

# Testing specific hypotheses with regression

Additional hierarchical multiple regressions conducted to address Reviewer 2's comments. This analysis was presented in the rebuttal but is not present in the article.

## Experiment 1

### Media

```{r}
#| label: "regression_exp1_media"
#| include: true

# Model without habit
model_exp1_media <- lm(Media ~ Impuls. + Stress + Eat + Comp., data = experiment_1_factors)
summary(model_exp1_media)

# Model with habit
model_exp1_media_habit <- lm(Media ~ Impuls. + Stress + Eat + Comp. + Automaticity + Routine, data = experiment_1_factors)
summary(model_exp1_media_habit)

# Model comparison
anova(model_exp1_media, model_exp1_media_habit)
```

### Compulsivity

```{r}
#| label: "regression_exp1_compulsivity"
#| include: true

# Model without habit
model_exp1_compulsivity <- lm(Comp. ~ Impuls. + Stress + Eat + Media, data = experiment_1_factors)
summary(model_exp1_compulsivity)

# Model with habit
model_exp1_compulsivity_habit <- lm(Comp. ~ Impuls. + Stress + Eat + Media + Automaticity + Routine, data = experiment_1_factors)
summary(model_exp1_compulsivity_habit)

# Model comparison
anova(model_exp1_compulsivity, model_exp1_compulsivity_habit)
```

## Experiment 2

### Media

```{r}
#| label: "regression_exp2_media"
#| include: true

# Model without habit
model_exp2_media <- lm(Media ~ Impuls. + Stress + Eat + Comp., data = experiment_2_factors)
summary(model_exp2_media)

# Model with habit
model_exp2_media_habit <- lm(Media ~ Impuls. + Stress + Eat + Comp. + Automaticity + Routine, data = experiment_2_factors)
summary(model_exp2_media_habit)

# Model comparison
anova(model_exp2_media, model_exp2_media_habit)
```

### Compulsivity

```{r}
#| label: "regression_exp2_compulsivity"
#| include: true

# Model without habit
model_exp2_compulsivity <- lm(Comp. ~ Impuls. + Stress + Eat + Media, data = experiment_2_factors)
summary(model_exp2_compulsivity)

# Model with habit
model_exp2_compulsivity_habit <- lm(Comp. ~ Impuls. + Stress + Eat + Media + Automaticity + Routine, data = experiment_2_factors)
summary(model_exp2_compulsivity_habit)

# Model comparison
anova(model_exp2_compulsivity, model_exp2_compulsivity_habit)
```

# Replication of Experiment 1 to Experiment 2

Additional analysis conducted with subset of questionnaires used in both Experiments 1 and 2 to address Reviewer 2's comments. This analysis can be found in the supporting information.

```{r}
#| label: "import_data_replication"
#| include: false

experiment_1_items <- readRDS(str_c(results_path, "/experiment_1_items.rds"))
experiment_2_items <- readRDS(str_c(results_path, "/experiment_2_items.rds"))
```

## Experiment 1

Since the PMPUQ is not present in Experiment 2, the first step is to get the factor structure of the network without the PMPUQ for Experiment 1.

### Extract factors from subscales

```{r} 
#| label: "efa_describe_1"
#| include: true

# Select subscales
var.subscales <- c("CESD_depressed",
                   "CESD_positive",
                   "CESD_somatic",
                   "CESD_relationship",
                   "EAT26_oral_control",
                   "EAT26_dieting",
                   "EAT26_bulimia",
                   "IAT_salience",
                   "IAT_excessive_use",
                   "IAT_neglect_work",
                   "IAT_anticipation",
                   "IAT_lack_control",
                   "IAT_neglect_social_life",
                   "OCIR_Washing",
                   "OCIR_checking",
                   "OCIR_ordering",
                   "OCIR_obsessing",
                   "OCIR_hoarding",
                   "OCIR_neutralising",
                   "PSS_total"
)

db.efa.exp1 <- experiment_1_items[var.subscales]
db.efa.descr1 = psych::describe(db.efa.exp1)

table_exp1_efa_descr <- knitr::kable(db.efa.descr1 , "html", caption = "Descriptive values for subscales used in Experiment 1") %>%
  kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp1_efa_descr 
```
Verify postulates with KMO and Barlett test:

```{r} 
#| label: "efa_postulates_1"
#| include: true

# Verify postulates
KMO(db.efa.exp1)

cor_matrix <- cor(db.efa.exp1, use = "complete.obs")

cortest.bartlett(cor_matrix, n = nrow(db.efa.exp1))
```

First, use parallel analysis method:

```{r} 
#| label: "efa_fa.parallel_1"
#| include: true

nFact  <- fa.parallel(db.efa.exp1, fm = "ml")
```

Second, use VSS method:

```{r} 
#| label: "efa_vss_1"
#| include: true

nFact  <- vss(db.efa.exp1) 
```
Third, nScree method:

```{r} 
#| label: "efa_nscreen_1"
#| include: true

nFact  <- nScree(x = na.omit(db.efa.exp1), model = "factors") 

plotnScree(nFact) 
```

Try method "comparisons data":

```{r} 
#| label: "efa_compdata_1"
#| include: true
 
nFact <- EFACompData(na.omit(db.efa.exp1), 8, n.pop = 10000, n.samples = 500, alpha = .30, graph = T,
                     corr.type = "pearson")
```

#### Apply EFA with 4 factors and an oblimin rotation

```{r} 
#| label: "efa_fa_1"
#| include: true

quest.1.efa1 <- fa(r = db.efa.exp1, nfactors =4, rotate = "oblimin", fm = "ml")

print(quest.1.efa1$loadings, cutoff = 0.2)
```

#### Compute factor scores 

We compute factor scores but importantly we assess factor indeterminacy to control if the factors can be used as predictors.

```{r} 
#| label: "efa_loading_1"
#| include: true

s.exp1 = factor.scores (db.efa.exp1, quest.1.efa1) #
s.exp1$R2
```
#### Plot correlation matrix between factors

```{r plot_correlation_matrix_1, echo=FALSE, warning=TRUE} 
fact_col_new  <- c( "CESD: depr.",
                   "CESD: pos.",
                   "CESD: somatic",
                   "CESD: relation.",
                   "EAT: oral contr.",
                   "EAT: dieting",
                   "EAT: bulimia",
                   "IAT: salience",
                   "IAT: exces. use",
                   "IAT: negl. work",
                   "IAT: anticip.",
                   "IAT: lack contr.",
                   "IAT: negl. social",
                   "OCI: wash.",
                   "OCI: check.",
                   "OCI: order.",
                   "OCI: obsess.",
                   "OCI: hoard.",
                   "OCI: neutr.",
                   "PSS")

col_old = var.subscales

colnames(db.efa.exp1)[colnames(db.efa.exp1) == var.subscales] <- fact_col_new
corrmatrix <- cor(db.efa.exp1, use="complete.obs")
col1 <- colorRampPalette(brewer.pal(9,"BrBG"))
corrplot(corrmatrix,method = "square", tl.col = "black", tl.cex = 0.75, sig.level = 0.05, insig = "pch", pch.cex = 1, col = col1(100))
# dev.print(pdf, file.path(figures_path,'Figure_Exp1_CorrelationalSyptomes_revision.pdf'))
# dev.off()
```
#### Extract transdiagnostic factors based on the EFA
```{r}
#| label: "plot_factor_loadings_1"
#| include: true
#| message: false
#| warning: false

# Get loadings into a dataset
load = quest.1.efa1$loadings
load = load[]
load = data.frame(load)
setDT(load,keep.rownames=TRUE)[]
colnames(load)[1] <- "Subscale"

loadings.m <- melt(load, id="Subscale",
                   measure=c("ML3", "ML1","ML2", "ML4"),
                   variable.name="Factor", value.name="Loading")


# Name factors
labels <- c(ML3 = "Media", ML1 = "Stress",
            ML2 = "Eat", ML4 = "Comp.")

loadings.m$subscales = fact_col_new

loadings.m$subscales <- factor(loadings.m$subscales, levels = loadings.m$subscales[seq (1:20)])

pp <- ggplot(loadings.m, aes(subscales, abs(Loading), fill=Loading)) +
  facet_wrap(~ Factor, nrow=1, labeller = labeller(Factor = labels) ) +
  geom_bar(stat="identity") + #make the bars
  coord_flip() + #flip the axes so the test names can be horizontal
  scale_fill_gradient2(name = "Loading",
                       high = "#006666", mid = "white", low = "goldenrod4",
                       midpoint=0, guide=F) +
  scale_x_discrete(limits = rev(levels(loadings.m$subscales)))+
  ylab("Loading Strength") +
  theme_bw(base_size=10)

# Make plot nicer
ppp <-   pp + theme_bw(base_size = 10, base_family = "Helvetica")+
  theme(strip.text.x = element_text(size = 15, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(color="white", fill="white", linetype="solid"),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

ppp

dev.print(pdf, file.path(figures_path, "experiment_1_factors_replication.pdf"))
dev.off()
```

#### Factors correlations

```{r}
#| label: "factor_correlation_1"
#| include: true
#| message: false
#| warning: false

var.net = c("COHS_automaticity", "COHS_routine","UPPS_total" )
db.network.tmp1 <- experiment_1_items[var.net]

# Merge with full database
axes.exp1 <- s.exp1$scores

# Combine
db.network.exp1 <- cbind(db.network.tmp1, axes.exp1)

# Rename with interpreted factors
old_names = c("COHS_automaticity", "COHS_routine", "UPPS_total",
               "ML1","ML3","ML2","ML4")

new_names <- c("Automaticity","Routine","Impuls.",
               "Stress","Media","Eat","Comp.")

colors <- c(pal[8], pal[8],pal[8],
            pal[9], pal[9], pal[9],
            pal[9])

colnames(db.network.exp1)[colnames(db.network.exp1) == old_names] <- new_names

# Descriptive correlation
factor_corr_plot <- cpplus(
  db.network.exp1,
  reorder=FALSE,
  alpha=0.05
  )

dev.print(pdf, file.path(figures_path, "experiment_1_factors_correlation_replication.pdf"))
dev.off()
```

### Dynamic network analysis

Centrality table:

```{r}
#| label: "network_centrality_1"
#| include: true

mynetwork.exp1 <- estimateNetwork(db.network.exp1, default ="EBICglasso") # EBIC hyperparameter is set to 0.5

CentralityTable <- centralityTable(mynetwork.exp1)

EITable <- subset(CentralityTable, measure == "ExpectedInfluence")

table_exp1_ei <- knitr::kable(EITable , "html", caption = "Centrality Table Experiment 1") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp1_ei
```

```{r}
#| label: "network_analysis_1"
#| include: true
#| message: false
#| warning: false

nledges <- getWmat(mynetwork.exp1)

plot_network.exp1 <- qgraph(nledges,
       layout = "spring",
       labels = new_names,
       label.scale = F,
       label.cex = 1,
       edge.labels = F,
       color = colors,
       border.color = colors,
       border.width = 4,
       node.width = 0.9,
       posCol = c("#006666","#006666"),
       negCol = c("goldenrod4","goldenrod4"),
       vTrans = 150,
       label.font = 2
       )

dev.print(pdf, file.path(figures_path, "experiment_1_network_revision.pdf"))
print(plot_network.exp1)
dev.off()
```

#### Estimate network edge weights accuracy and centrality measures stability

First for edges:

```{r}
#| label: "network_stability_edges_1"
#| include: true
#| message: false
#| warning: false

set.seed(1331)
b1 <- bootnet(mynetwork.exp1,  nBoots= 10000, nCores = 1,
              statistics = c("strength","expectedInfluence","edge"),caseN = 50)

tb.b1 = summary(b1)

table_exp1_boot <- knitr::kable(tb.b1 , "html", caption = "Table Experiment 1") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp1_boot

plot (b1, plot = "interval", split0 = TRUE, order="sample", labels=T)
```

And for centrality indices:

```{r}
#| label: "network_stability_1"
#| include: true
#| message: false
#| warning: false

set.seed(1331)
b2 <- bootnet(mynetwork.exp1,nBoots= 10000, nCores = 1, type = "case",
              statistics = c("strength","expectedInfluence","edge"),caseN = 50)

corStability(b2)

plot (b2, c("expectedInfluence")) # Centrality stability graph
```

## Experiment 2

### Extract factors from subscales

```{r}
#| label: "efa_describe_2"
#| include: true
#| message: false
#| warning: false

# Select subscales
var.subscales <- c("CESD_depressed",
                   "CESD_positive",
                   "CESD_somatic",
                   "CESD_relationship",
                   "EAT26_oral_control",
                   "EAT26_dieting",
                   "EAT26_bulimia",
                   "IAT_salience",
                   "IAT_excessive_use",
                   "IAT_neglect_work",
                   "IAT_anticipation",
                   "IAT_lack_control",
                   "IAT_neglect_social_life",
                   "OCIR_washing",
                   "OCIR_checking",
                   "OCIR_ordering",
                   "OCIR_obsessing",
                   "OCIR_hearding",
                   "OCIR_neutralising",
                   "PSS_total")

# db.subscales <- experiment_2_items[var.subscales]
db.efa.exp2 <- experiment_2_items[var.subscales]

db.efa.descr2 = psych::describe(db.efa.exp2)

table_exp2_efa_descr <- knitr::kable(db.efa.descr2 , "html", caption = "Descriptive values for subscales used in Experiment 2") %>%
  kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp2_efa_descr 
```

Verify postulates with KMO and Bartlett test:

```{r}
#| label: "efa_postulates_2"
#| include: true
#| message: false
#| warning: false

KMO (db.efa.exp2)

cor_matrix <- cor(db.efa.exp2, use = "complete.obs")

cortest.bartlett(cor_matrix, n = nrow(db.efa.exp2))
```

First, use parallel analysis method:

```{r} 
#| label: "efa_fa.parallel_2"
#| include: true
#| message: false
#| warning: false

nFact  <- fa.parallel(db.efa.exp2, fm = "ml") 
```

Second, use VSS method:
 
```{r} 
#| label: "efa_vss_2"
#| include: true
#| message: false
#| warning: false

nFact <- vss(db.efa.exp2)
```

Third, nScree method:

```{r} 
#| label: "efa_nscreen_2"
#| include: true
#| message: false
#| warning: false

nFact  <- nScree(x = na.omit(db.efa.exp2), model = "factors") 
plotnScree(nFact) 
```

Try method "comparisons data":

```{r} 
#| label: "efa_compdata_2"
#| include: true
#| message: false
#| warning: false

nFact <- EFACompData(na.omit(db.efa.exp2), 10, n.pop = 10000, n.samples = 500, alpha = .30, graph = T,corr.type = "pearson") 
```

#### Apply EFA with oblimin rotation

```{r} 
#| label: "efa_fa_2"
#| include: true
#| message: false
#| warning: false

quest.sc.efa2 <- fa(r = db.efa.exp2, nfactors =4, rotate = "oblimin", fm = "ml") 
print(quest.sc.efa2$loadings,cutoff = 0.2)
```

#### Compute factor scores 

We compute factor scores but importantly we assess factor indeterminacy to control if the factors can be used as predictors.

```{r} 
#| label: "efa_loading_2"
#| include: true
#| message: false
#| warning: false

s.exp2 = factor.scores (db.efa.exp2, quest.sc.efa2) 
s.exp2$R2
```
 
#### Plot correlation matrix of all subscales
 
```{r}
#| label: "plot_correlation_matrix_2"
#| include: true
#| message: false
#| warning: false

fact_col_new  <- c( "CESD: depr.",
                   "CESD: pos.",
                   "CESD: somatic",
                   "CESD: relation.",
                   "EAT: oral contr.",
                   "EAT: dieting",
                   "EAT: bulimia",
                   "IAT: salience",
                   "IAT: exces. use",
                   "IAT: negl. work",
                   "IAT: anticip.",
                   "IAT: lack contr.",
                   "IAT: negl. social",
                   "OCI: wash.",
                   "OCI: check.",
                   "OCI: order.",
                   "OCI: obsess.",
                   "OCI: hoard.",
                   "OCI: neutr.",
                   "PSS")

col_old = var.subscales

colnames(db.efa.exp2)[colnames(db.efa.exp2) == var.subscales] <- fact_col_new
corrmatrix <- cor(db.efa.exp2, use="complete.obs")
col1 <- colorRampPalette(brewer.pal(9,"BrBG"))
corrplot(corrmatrix,method = "square", tl.col = "black", tl.cex = 0.5, sig.level = 0.05, insig = "pch", pch.cex = 1, col = col1(100))
dev.print(pdf, file.path(figures_path, "experiment_2_correlation_matrix_replication.pdf"))
dev.off()
```
 
#### Extract transdiagnostic factors based on the EFA
 
```{r} 
#| label: "plot_factor_loadings_2"
#| include: true
#| message: false
#| warning: false

# Get loadings into a dataset
load = quest.sc.efa2$loadings
load = load[]
load = data.frame(load)
setDT(load,keep.rownames=TRUE)[]
colnames(load)[1] <- "Subscale"

loadings.m <- melt(load, id="Subscale",
                   measure=c("ML3", "ML2","ML1", "ML4"),
                   variable.name="Factor", value.name="Loading")

# Name factors
labels <- c(ML3 = "Media", ML1 = "Eat",
            ML2 = "Stress", ML4 = "Comp.")

loadings.m$subscales = fact_col_new

loadings.m$subscales <- factor(loadings.m$subscales, levels = loadings.m$subscales[seq (1:20)])

pp <- ggplot(loadings.m, aes(subscales, abs(Loading), fill=Loading)) +
  facet_wrap(~ Factor, nrow=1, labeller = labeller(Factor = labels) ) +
  geom_bar(stat="identity") + #make the bars
  coord_flip() + #flip the axes so the test names can be horizontal
  scale_fill_gradient2(name = "Loading",
                       high = "#006666", mid = "white", low = "goldenrod4",
                       midpoint=0, guide=F) +
  scale_x_discrete(limits = rev(levels(loadings.m$subscales)))+
  ylab("Loading Strength") +
  theme_bw(base_size=10)

# Make plot nicer
ppp <-   pp + theme_bw(base_size = 10, base_family = "Helvetica")+
  theme(strip.text.x = element_text(size = 15, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(color="white", fill="white", linetype="solid"),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

ppp

dev.print(pdf, file.path(figures_path, "experiment_2_factors_replication.pdf"))
dev.off()
```
 
#### Factors correlations

```{r} 
#| label: "factor_correlation_2"
#| include: true
#| message: false
#| warning: false

var.net = c("COHS_automaticity", "COHS_routine", "UPPS_total" )
db.network.tmp2 <- experiment_2_items[var.net]

# Merge with full database
axes.exp2 <- s.exp2$scores

# Combine
db.network.exp2 <- cbind(db.network.tmp2, axes.exp2)

# Rename with interpreted factors
old_names = c("COHS_automaticity", "COHS_routine","UPPS_total",
               "ML2", "ML3","ML4", "ML1")

new_names <- c("Automaticity","Routine","Impuls.",
               "Stress", "Media", "Comp.", "Eat")
 
colors <- c(pal[8], pal[8],pal[8],
            pal[9], pal[9], pal[9],
            pal[9])

colnames(db.network.exp2)[colnames(db.network.exp2) == old_names] <- new_names

# Descriptive correlation
factor_corr_plot <- cpplus(db.network.exp2, reorder=FALSE, alpha=0.05)

dev.print(pdf, file.path(figures_path, "experiment_2_factors_correlation_replication.pdf"))
dev.off()
```
 
### Dynamic network analysis

Centrality table:

```{r} 
#| label: "network_centrality_2"
#| include: true
#| message: false
#| warning: false

# Estimate network
mynetwork.exp2 <- estimateNetwork(db.network.exp2, default ="EBICglasso") # Lasso with ebic hyperparameter is 0.5

CentralityTable <- centralityTable(mynetwork.exp2)

EITable <- subset(CentralityTable, measure == "ExpectedInfluence")

table_exp2_ei <- knitr::kable(EITable , "html", caption = "Centrality Table Experiment 2") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp2_ei
```

```{r} 
#| label: "network_plot_2"
#| include: true
#| message: false
#| warning: false

nledges <- getWmat(mynetwork.exp2)

plot_network.exp2 <- qgraph(nledges,
       layout = "spring",
       labels = new_names,
       label.scale = F,
       label.cex = 1,
       edge.labels = F,
       #cut = 0.1,
       color = colors,
       border.color = colors,
       border.width = 4,
       node.width = 0.9,
       posCol = c("#006666","#006666"),
       negCol = c("goldenrod4","goldenrod4"),
       vTrans = 150,
       label.font = 2
       )

dev.print(pdf, file.path(figures_path, "experiment_2_network_replication.pdf"))
print(plot_network.exp2)
dev.off()
```

#### Estimate the network stability

First for edges:

```{r} 
#| label: "network_stability_edges_2"
#| include: true
#| message: false
#| warning: false

# Set seed to obtain reproducible results
set.seed(1331)
b1 <- bootnet(mynetwork.exp2, nBoots= 10000, nCores = 1,
              statistics = c("strength","expectedInfluence","edge"),caseN = 50)

tb.b1 = summary(b1)

table_exp2_boot <- knitr::kable(tb.b1 , "html", caption = "Table Experiment 2") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

table_exp2_boot

plot (b1, plot = "interval", split0 = TRUE, order="sample", labels=T)
```

And for centrality indices:

```{r} 
#| label: "network_stability_centrality_2"
#| include: true
#| message: false
#| warning: false

set.seed(1331)
b2 <- bootnet(mynetwork.exp2, nBoots= 10000, nCores = 1, type = "case",
              statistics = c("strength","expectedInfluence","edge"),caseN = 50)

corStability(b2)

plot (b2, c("expectedInfluence")) # Centrality stability graph
```
 
# Adding cutoff values to questionnaire distributions

```{r}
#| label: "import_data_cutoffs"
#| include: false

experiment_1_questionnaires <- readRDS(str_c(results_path, "/experiment_1_questionnaires.rds"))
experiment_2_questionnaires <- readRDS(str_c(results_path, "/experiment_2_questionnaires.rds"))
```

## Experiment 1

```{r}
#| label: "plot_distribution_experiment_1"
#| echo: true

# Labels
labels <- c(CESD_total = "CES-D", 
            COHS_total = "COHS",
            EAT26_total = "EAT", 
            IAT_total = "IAT", 
            PSS_total = "PSS",
            OCIR_total = "OCI", 
            UPPS_total = "UPPS",
            STAIT_total = "STAI-T",
            PMPUQSV_total = "PMPUQ")

cutoff_values <- tribble(
  ~questionnaire, ~cutoff,
  # CES-D
  # Morin, A. J. S., Moullec, G., Maïano, C., Layet, L., Just, J.-L., & Ninot, 
  # G. (2011). Psychometric properties of the Center for Epidemiologic Studies 
  # Depression Scale (CES-D) in French clinical and nonclinical adults. Revue 
  # d’Épidémiologie et de Santé Publique, 59(5), 327–340.
  # https://doi.org/10.1016/j.respe.2011.03.061
  "CESD_total",   19,

  # EAT
  # Leichner, P., Steiger, H., & Gottheil, N. (1994). Validation d’une échelle
  # d’attitudes alimentaires auprès d’une population québécoise francophone. 
  # 39(1).
  "EAT26_total",  20,
  
  # IAT
  # Khazaal, Y., Billieux, J., Thorens, G., Khan, R., Louati, Y., Scarlatti,
  # E., Theintz, F., Lederrey, J., Van Der Linden, M., & Zullino, D. (2008). 
  # French Validation of the Internet Addiction Test. CyberPsychology & 
  # Behavior, 11(6), 703–706. https://doi.org/10.1089/cpb.2007.0249
  "IAT_total",    50,
  
  # OCI-R
  # Abramowitz, J. S., & Deacon, B. J. (2006). Psychometric properties and 
  # construct validity of the Obsessive–Compulsive Inventory—Revised: 
  # Replication and extension with a clinical sample. Journal of Anxiety 
  # Disorders, 20(8), 1016–1035. https://doi.org/10.1016/j.janxdis.2006.03.001
  "OCIR_total",   14,
  
  # PMPUQ
  # No cutoff score exists
  # Harris, B., Regan, T., Schueler, J., & Fields, S. A. (2020). Problematic 
  # Mobile Phone and Smartphone Use Scales: A Systematic Review. Frontiers in 
  # Psychology, 11. https://doi.org/10.3389/fpsyg.2020.00672
  
  # PSS
  # No cutoff score exists
  # We could use the normative data from the French PSS-10
  
  # STAI
  # Wiglusz, M. S., Landowski, J., & Cubała, W. J. (2019). Psychometric 
  # properties and diagnostic utility of the State–Trait Anxiety Inventory in
  # epilepsy with and without comorbid anxiety disorder. Epilepsy & Behavior, 
  # 92, 221–225. https://doi.org/10.1016/j.yebeh.2019.01.005
  "STAIT_total", 52
  
  # UPPS
  # No cutoff score exists
)

# Plot questionnaire distributions
pp <- ggplot(data = experiment_1_questionnaires, aes (x = score, fill = questionnaire)) +
  facet_wrap(
    ~ questionnaire,
    scales = "free",
    labeller = labeller(questionnaire = labels)
    ) +
  geom_histogram(aes(y=..density..), alpha=0.6) +
  geom_density(aes(color = questionnaire), alpha = 0.3) +
  geom_vline(
    data = cutoff_values, 
    mapping = aes(xintercept = cutoff),
    linetype = "dashed") +
  scale_fill_viridis_d(
    name = "Questionnaires", 
    begin = .1, end = .9,
    option = "inferno",
    aesthetics = c("color", "fill"),
    labels = labels) +
  theme_bw() +
  labs(
    title = "",
    x = "Experiment 1 questionnaires",
    y = "Frequency"
  )

# Plot formatting
ppp_1 <- pp +
  theme_bw(base_size = 10, base_family = "Helvetica") +
  theme(
    strip.text.x = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(color = "white", fill= "white", linetype = "solid"),
    axis.ticks.x = element_blank(),
    axis.text.x  = element_blank(),
    axis.title.x = element_text(size = 13, margin = margin(103)),
    axis.title.y = element_text(size = 13),
    legend.position = "none"
    # plot.margin = margin(5.5, 5.5, 90, 5.5)
    )

ppp_1
```

## Experiment 2

### Manual coding

```{r}
#| label: "gas_cutoff"
#| echo: true

# Khazaal, Y., Chatton, A., Rothen, S., Achab, S., Thorens, G., Zullino, D.,
# & Gmel, G. (2016). Psychometric properties of the 7-item game addiction scale 
# among french and German speaking adults. BMC Psychiatry, 16(1), 132. 
# https://doi.org/10.1186/s12888-016-0836-3

# In accordance with the hypothesis of Lemmens et al. [44], those who scored 
# “sometimes” or more on all seven items were defined as monothetic gamers 
# (“pathological gaming”), and those who scored “sometimes” or more on at least 
# half of the items (four to six of seven items) were defined as polythetic 
# gamers (excessive gaming).

gas <- experiment_2_items %>%
  select(starts_with("GAS")) %>%
  mutate(
    excessive_1 = case_when(
      `GAS[1]` >= 3 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    excessive_2 = case_when(
      `GAS[2]` >= 3 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    excessive_3 = case_when(
      `GAS[3]` >= 3 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    excessive_4 = case_when(
      `GAS[4]` >= 3 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    excessive_5 = case_when(
      `GAS[5]` >= 3 ~ 1,
      .default = 0
    )
  ) %>%  
  mutate(
    excessive_6 = case_when(
      `GAS[6]` >= 3 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    excessive_7 = case_when(
      `GAS[7]` >= 3 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    excessive_total = excessive_1 + excessive_2 + excessive_3 + excessive_4 + excessive_5 + excessive_6 + excessive_7
  ) %>%
  mutate(
    excessive = case_when(
      excessive_total >= 4 ~ 1,
      .default = 0
    )
  )

# Get number of excessive gamers
n_excessive <- gas$excessive %>%
  plyr::count() %>%
  filter(x == 1) %>%
  select(freq)
  
# Calculate cutoff that will result in the correct proportion of individuals
# being classified on the plot
cutoff_gas <- sort(gas$GAS_total) %>%
  nth(., (nrow(gas) - as.integer(n_excessive)))
```

```{r}
#| label: "eds_cutoff"
#| echo: true

# Hausenblas, H. A., & Downs, D. S. (2002). How Much is Too Much? The 
# Development and Validation of the Exercise Dependence Scale. Psychology & 
# Health, 17(4), 387–404. https://doi.org/10.1080/0887044022000004894

# Individuals who indicate strong endorsement (i.e., 5 or 6 on the Likert scale)
# on at least three of the seven criteria are classified as at-risk.

eds <- experiment_2_items %>%
  select(starts_with("EDSR_")) %>%
  mutate(
    tolerance = case_when(
      EDSR_tolerance >= 15 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    withdrawal = case_when(
      EDSR_withdrawal >= 15 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    lack_control = case_when(
      EDSR_lack_control >= 15 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    time = case_when(
      EDSR_time >= 15 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    reduction_activities = case_when(
      EDSR_reduction_activities >= 15 ~ 1,
      .default = 0
    )
  ) %>%  
  mutate(
    intention = case_when(
      EDSR_intention >= 15 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    continuance = case_when(
      EDSR_continuance >= 15 ~ 1,
      .default = 0
    )
  ) %>%
  mutate(
    at_risk_total = tolerance + withdrawal + lack_control + time + reduction_activities + intention + continuance
  ) %>%
  mutate(
    at_risk = case_when(
      at_risk_total >= 3 ~ 1,
      .default = 0
    )
  )

# Get number of individuals at risk for exercise dependence
n_at_risk <- eds$at_risk %>%
  plyr::count() %>%
  filter(x == 1) %>%
  select(freq)
  
# Calculate cutoff that will result in the correct proportion of individuals
# being classified on the plot
cutoff_eds <- sort(eds$EDSR_total) %>%
  nth(., (nrow(eds) - as.integer(n_at_risk)))
```

```{r}
#| label: "myfas_cutoff"
#| echo: true

# Brunault, P., Berthoz, S., Gearhardt, A. N., Gierski, F., Kaladjian, A., 
# Bertin, E., Tchernof, A., Biertho, L., De Luca, A., Hankard, R., Courtois, 
# R., Ballon, N., Benzerouk, F., & Bégin, C. (2020). The Modified Yale Food 
# Addiction Scale 2.0: Validation Among Non-Clinical and Clinical 
# French-Speaking Samples and Comparison With the Full Yale Food Addiction 
# Scale 2.0. Frontiers in Psychiatry, 11, 480671. 
# https://doi.org/10.3389/fpsyt.2020.480671
# https://sites.lsa.umich.edu/fastlab/yale-food-addiction-scale/

# Mild Food Addiction = 2 or 3 symptoms and clinical significance
yfas <- experiment_2_items %>%
  select(starts_with("YFAS")) %>%
  mutate(
    addiction = case_when(
      YFAS_score >= 2 & YFAS_clinical_sign == 1 ~ 1,
      .default = 0
    )
  )

# Get number of excessive gamers
n_addiction <- yfas$addiction %>%
  plyr::count() %>%
  filter(x == 1) %>%
  select(freq)
  
# Calculate cutoff that will result in the correct proportion of individuals
# being classified on the plot
cutoff_yfas <- sort(yfas$YFAS_score) %>%
  nth(., (nrow(eds) - as.integer(n_addiction)))
```

```{r}
#| label: "plot_distribution_experiment_2"
#| echo: true

# Labels
labels <- c(EAT26_total = "EAT", 
            COHS_total = "COHS",
            PSS_total = "PSS",
            IAT_total = "IAT", 
            PCLS_total = "PCLS", 
            OCIR_total = "OCI", 
            STICSAT_total = "STICSA-T",
            UPPS_total = "UPPS",
            SASSV_total ="SASSV" ,
            GAS_total = "GAS",
            EDSR_total = "EDS",
            LSAS_total = "LSAS",
            YFAS_score = "mYFAS",
            QABB_total = "QABB",
            CESD_total = "CES-D")

cutoff_values <- tribble(
  ~questionnaire, ~cutoff,
  # CES-D
  # Morin, A. J. S., Moullec, G., Maïano, C., Layet, L., Just, J.-L., & Ninot, 
  # G. (2011). Psychometric properties of the Center for Epidemiologic Studies 
  # Depression Scale (CES-D) in French clinical and nonclinical adults. Revue 
  # d’Épidémiologie et de Santé Publique, 59(5), 327–340.
  # https://doi.org/10.1016/j.respe.2011.03.061
  "CESD_total",   19,

  # EAT
  # Leichner, P., Steiger, H., & Gottheil, N. (1994). Validation d’une échelle
  # d’attitudes alimentaires auprès d’une population québécoise francophone. 
  # 39(1).
  "EAT26_total",  20,
  
  # IAT
  # Khazaal, Y., Billieux, J., Thorens, G., Khan, R., Louati, Y., Scarlatti,
  # E., Theintz, F., Lederrey, J., Van Der Linden, M., & Zullino, D. (2008). 
  # French Validation of the Internet Addiction Test. CyberPsychology & 
  # Behavior, 11(6), 703–706. https://doi.org/10.1089/cpb.2007.0249
  "IAT_total",    50,
  
  # OCI-R
  # Abramowitz, J. S., & Deacon, B. J. (2006). Psychometric properties and 
  # construct validity of the Obsessive–Compulsive Inventory—Revised: 
  # Replication and extension with a clinical sample. Journal of Anxiety 
  # Disorders, 20(8), 1016–1035. https://doi.org/10.1016/j.janxdis.2006.03.001
  "OCIR_total",   14,
  
  # PMPUQ
  # No cutoff score exists
  # Harris, B., Regan, T., Schueler, J., & Fields, S. A. (2020). Problematic 
  # Mobile Phone and Smartphone Use Scales: A Systematic Review. Frontiers in 
  # Psychology, 11. https://doi.org/10.3389/fpsyg.2020.00672
  
  # PSS
  # No cutoff score exists
  # We could use the normative data from the French PSS-10
  
  # UPPS
  # No cutoff score exists
  
  # EDS-R
  # No cutoff score, but calculation to determine if at-risk of dependence
  "EDSR_total", cutoff_eds,
  
  # GAS
  # No cutoff score, but calculation to determine if excessive above
  "GAS_total", cutoff_gas,

  # LSAS
  # Caballo, V. E., Salazar, I. C., Arias, V., Hofmann, S. G., & Curtiss, J. 
  # (2018). Psychometric properties of the Liebowitz Social Anxiety Scale in a 
  # large cross-cultural Spanish and Portuguese speaking sample. Brazilian 
  # Journal of Psychiatry, 41, 122–130. 
  # https://doi.org/10.1590/1516-4446-2018-0006
  "LSAS_total", 60,
  
  # PCLS
  # Blanchard, E. B., Jones-Alexander, J., Buckley, T. C., & Forneris, 
  # C. A. (1996). Psychometric properties of the PTSD checklist (PCL). Behaviour
  # Research and Therapy, 34(8), 669–673.
  # https://doi.org/10.1016/0005-7967(96)00033-2
  "PCLS_total", 44,
  
  # QABB
  # Lejoyeux, M., Mathieu, K., Embouazza, H., Huet, F., & Lequen, V. (2007). 
  # Prevalence of compulsive buying among customers of a Parisian general store.
  # Comprehensive Psychiatry, 48(1), 42–46. 
  # https://doi.org/10.1016/j.comppsych.2006.05.005
  "QABB_total", 10,
  
  # SASSV
  # Lopez-Fernandez, O. (2017). Short version of the Smartphone Addiction Scale 
  # adapted to Spanish and French: Towards a cross-cultural research in 
  # problematic mobile phone use. Addictive Behaviors, 64, 275–280. 
  # https://doi.org/10.1016/j.addbeh.2015.11.013
  "SASSV_total", 32,
  
  # STICSA-T
  # Van Dam, N. T., Gros, D. F., Earleywine, M., & Antony, M. M. (2013). 
  # Establishing a trait anxiety threshold that signals likelihood of anxiety 
  # disorders. Anxiety, Stress, & Coping, 26(1), 70–86. 
  # https://doi.org/10.1080/10615806.2011.631525
  "STICSAT_total", 43,
  
  # YFAS
  # No cutoff score, but calculation to determine if addiction present above
  "YFAS_score", cutoff_yfas
)

# Plot questionnaire distributions
pp <- ggplot(data = experiment_2_questionnaires, aes (x = score, fill = questionnaire)) +
  facet_wrap(
    ~ questionnaire,
    scales = "free",
    labeller = labeller(questionnaire = labels)
    ) +
  geom_histogram(aes(y=..density..), alpha=0.6) +
  geom_density(aes(color = questionnaire), alpha = 0.3) +
  geom_vline(
    data = cutoff_values, 
    mapping = aes(xintercept = cutoff),
    linetype = "dashed") +
  scale_fill_viridis_d(
    name = "Questionnaires", 
    begin = .1, end = .9,
    option = "inferno",
    aesthetics = c("color", "fill"),
    labels = labels) +
  theme_bw() +
  labs(
    title = "",
    x = "Experiment 2 questionnaires",
    y = ""
  )

# Plot formatting
ppp_2 <- pp + 
  theme_bw(base_size = 10, base_family = "Helvetica") +
  theme(
    strip.text.x = element_text(size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(color = "white", fill = "white", linetype = "solid"),
    axis.ticks.x = element_blank(),
    axis.text.x  = element_blank(),
    axis.title.x = element_text(size = 13),
    axis.title.y = element_text(size = 13),
    legend.position = "none"
    )

ppp_2
```

## Create joint figure

```{r}
#| label: "plot_questionnaire_distribution_both"
#| echo: true

p <- ggarrange(
  ppp_1, ppp_2, labels = c("A", "B"),
  widths = c(1, 1.3)
  )

ggsave(
  filename = str_c(
    figures_path, "/questionnaires_distribution_revision.pdf"),
  plot = p,
  height = 6,
  width = 11)
```

# Create joint figure of COHS subscales

```{r}
#| label: "plot_cohs_distribution_both"
#| echo: true

experiment_1_cohs <- readRDS(str_c(results_path, "/experiment_1_cohs.rds"))
experiment_2_cohs <- readRDS(str_c(results_path, "/experiment_2_cohs.rds"))

labels <- c(routine = "COHS Routine",
            automaticity = "COHS Automaticity",
            total = "COHS Total")

# Plot Experiment 1
pp_1 = ggplot(data = experiment_1_cohs, aes (x = value, fill = scale)) +
  facet_wrap(~scale, scales = "free", labeller = labeller(scale = labels)) +
  geom_histogram(aes(y=..density..),alpha=0.6) +
  geom_density(aes(color = scale), alpha = 0.3) +
    scale_fill_viridis_d(name = "Questionnaires", 
                       begin = .1, end = .9,
                       option = "inferno",
                       aesthetics = c("color", "fill"),
                       labels = labels)+
  theme_bw()+
  labs(
    title = '',
    x = "Experiment 1",
    y = "Frequency"
  )

# Make plot nicer
ppp_1 <-   pp_1 + theme_bw(base_size = 10, base_family = "Helvetica")+
  theme(strip.text.x = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(color="white", fill="white", linetype="solid"),
        axis.title.x = element_text(size = 15, face = "bold"),
        axis.title.y = element_text(size = 15, face = "bold"),
        legend.position = "none")

# Plot Experiment 2
pp_2 = ggplot(data = experiment_2_cohs, aes (x = value, fill = scale)) +
  facet_wrap(~scale, scales = "free", labeller = labeller(scale = labels)) +
  geom_histogram(aes(y=..density..),alpha=0.6) +
  geom_density(aes(color = scale), alpha = 0.3) +
    scale_fill_viridis_d(name = "Questionnaires", 
                       begin = .1, end = .9,
                       option = "inferno",
                       aesthetics = c("color", "fill"),
                       labels = labels)+
  theme_bw()+
  labs(
    title = '',
    x = "Experiment 2",
    y = "Frequency"
  )

# Make plot nicer
ppp_2 <-   pp_2 + theme_bw(base_size = 10, base_family = "Helvetica")+
  theme(strip.text.x = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(color="white", fill="white", linetype="solid"),
        # axis.ticks.x = element_blank(),
        # axis.text.x  = element_blank(),
        axis.title.x = element_text(size = 15, face = "bold"),
        axis.title.y = element_text(size = 15, face = "bold"),
        legend.position = "none")

# Create joint figure
p <- ggarrange(
  ppp_1, ppp_2, labels = c("A", "B"), align = "v",
  nrow = 2,
  widths = c(1, 1.3)
  )
p

ggsave(
  filename = str_c(
    figures_path, "/cohs_distribution_revision.pdf"),
  plot = p,
  height = 6,
  width = 11)
```