---
title: "Differential influence of habit components on problematic behaviors - Symptom network analysis"
author: "Lavinia Wuensch, Yoann Stussi, Théo Vernede, Eva R. Pool"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

# Symptom network analysis

```{r setup, echo=TRUE, message= FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

# Load libraries
library(here)
library(car)
library(afex)
library(doBy)
library(ggplot2)
library(viridis)
library(ggExtra)
library(viridis)
library(jtools)
library(plyr)
library(dplyr)
library(tidyr)
library(psych)
library(devtools)
library(GPArotation)
library(nFactors)
library(RGenData)
library(lavaan)
library(semPlot)
library(data.table)
library(reshape2)
library(Hmisc)

# For network analysis
library(corrplot)
library(RColorBrewer)
library(bootnet)
library(networktools)
library(NetworkComparisonTest)
library(qgraph)

# For html file 
library(JWileymisc)
library(kableExtra)
library(knitr)
```

```{r loaddata, include = FALSE}
# Set up paths
data_path <- here::here("databases")
figures_path <- here::here("figures")
utilities_path <- here::here("analysis", "functions")

source(file.path(utilities_path,'cpplus.r'))
source(file.path(utilities_path,'setup.r'))
```

```{r get_symptoms, include=FALSE}
# Depression
col = paste("CESD[",1:20,"]", sep="") 
CESD1 = Q1[col]
CESD2 = Q2[col]

CESD = rbind(CESD1, CESD2)

# Stress
col = paste("PSS[",1:10,"]", sep="") 
PSS2= Q2[col]
PSS1= Q1[col]

PSS = rbind(PSS1, PSS2)

# OCD
col = paste("OCIR[",1:18,"]", sep="") 
OCIR1 =  Q1[col]
OCIR2 =  Q2[col]

OCIR = rbind(OCIR1, OCIR2)

# Problematic internet
col = paste("IAT[",1:20,"]", sep="") 
IAT1=  Q1[col]
IAT2=  Q2[col]

IAT = rbind(IAT1, IAT2)

# Problematic eating
col = paste("EAT26[",1:26,"]", sep="") 
EAT261=  Q1[col]
EAT262=  Q2[col]

EAT26 = rbind(EAT261, EAT262)

# COHS automaticity
COHS_automaticity1 = Q1["COHS_automaticity"]
COHS_automaticity2 = Q2["COHS_automaticity"]

COHS_automaticity = rbind(COHS_automaticity1, COHS_automaticity2)

# COHS routine
COHS_routine1 = Q1["COHS_routine"]
COHS_routine2 = Q2["COHS_routine"]

COHS_routine = rbind(COHS_routine1, COHS_routine2)
```


```{r count_included_participants}
sub1 = Q1["sub"]
sub2 = Q2["sub"]

sub = rbind(sub1, sub2)

# Combine datasets
db.sympt  = cbind (CESD, PSS, IAT, EAT26, OCIR, COHS_automaticity, COHS_routine, sub)
db.sympt.sub = na.omit(db.sympt)

# Count participants
count.participants <- plyr::count(db.sympt.sub, c("sub"))
sum(count.participants$freq)
```

# Identify communities

We want to get the color code for our symptoms groups into clusters

```{r network_clusters, echo=TRUE, message= FALSE, warning= FALSE}
# Create dataset for analysis
db.sympt.all<- subset( db.sympt.sub, select = -sub )

# Combine dataset
db.sympt  = cbind (CESD, PSS, IAT, EAT26, OCIR)

# Get clusters to color code symptoms
sympt.ega.simple <- EGAnet::EGA(db.sympt, model = "glasso")
```

# Compute the network

```{r network, echo=TRUE, message= FALSE, warning= FALSE}
# Create color code based on the  communities
colors = c(rep(pal_sy[9],30), rep(pal_sy[10],20), rep(pal_sy[6],26), rep(pal_sy[4],18),rep(pal[8],2)) 
new_names = c(paste("cesd",1:20,"", sep="") , paste("pss",1:10,"", sep=""), paste("iat",1:20,"", sep=""), paste("eat",1:26,"", sep=""),paste("oci",1:18,"", sep=""), "Automaticity", "Routine") 

mynetwork.sympt <- estimateNetwork(db.sympt.all, default ="EBICglasso") 
nledges.sympt   <- getWmat(mynetwork.sympt)

# Plot network
qgraph(nledges.sympt,
       minimum = 0.05,
       cut = 0.1,
       layout = "spring",
       label.scale = F,
       label.norm = 12,
       labels = new_names,
       label.cex = 0.7,
       edge.labels = F,
       border.width = 2,
       color = colors,
       border.color = colors,
       node.width = 1.2,
       posCol = c("#006666","#006666"),
       negCol = c("goldenrod4","goldenrod4"),
       vTrans = 160,
       label.font = 2)

dev.print(pdf, file.path(figures_path, "experiment_1_2_symptoms_network.pdf"))
dev.off()

CentralityTable <- centralityTable(mynetwork.sympt)
```

Assess the precision of edge estimations for automaticity:

```{r edges_precision_automaticity, echo=TRUE, message= FALSE, warning= FALSE}
# Estimate network stability
set.seed(1331)
b1 <- bootnet(mynetwork.sympt, boots= 10000, nCores = 1,
              statistics = c("strength","expectedInfluence","edge"),caseN = 50)

# Put values in a tables
tb.b1 = summary(b1)

# Get values of interest
automaticity = subset(tb.b1, type == "edge" & node1 == "COHS_automaticity" | node2 =="COHS_automaticity")

tb_symp_auto <- automaticity %>% as.data.frame() %>% arrange(desc(sample))

tb_symp_auto_boot <- knitr::kable(tb_symp_auto , "html", caption = "Table Automaticity") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

tb_symp_auto_boot
```

Assess the precision edge estimations for routine:

```{r edges_precision_routine, echo=TRUE, message= FALSE, warning= FALSE}
# Get values of interest
routine = subset(tb.b1, type == "edge" & node1 == "COHS_routine" | node2 =="COHS_routine")

tb_symp_routine <- routine  %>% as.data.frame() %>% arrange(desc(sample))

tb_symp_routine_boot <- knitr::kable(tb_symp_routine, "html", caption = "Table Routine") %>%
 kableExtra::kable_styling(latex_options = "HOLD_position", position = "center", full_width = F) %>%
  row_spec(0,bold=T,align='c')

tb_symp_routine_boot
```

Estimate centrality index stability:

```{r network_stability, echo=TRUE, message= FALSE, warning= FALSE}
set.seed(1331)
b2 <- bootnet(mynetwork.sympt, boots= 10000, nCores = 1, type = "case",
              statistics = c("strength","expectedInfluence","edge"),caseN = 50)

set.seed(1331)
b3 <- bootnet(mynetwork.sympt, boots= 10000, nCores = 1, type = "case",
              statistics = c("Strength","Betweenness","Closeness"),caseN = 50)

corStability(b3)
plot(b3, c("Strength","Betweenness","Closeness"))

corStability(b2)
plot (b2, c("strength"))
plot (b2, c("edge"))
plot (b2, c("expectedInfluence"))

# Edge precision
plot (b1, labels= F, order = "sample")

# Strength centrality 
plot (b1, "strength", order = "sample", label = TRUE)

# Expected influence centrality
plot(b1, "expectedInfluence", order = "sample", label = T)
```

Compute bridge symptoms -- this is not reported in the main manuscript

```{r bridge, echo=TRUE, message= FALSE, warning= FALSE}
#my_groups = list("STR"=c(1:30),"INT"=c(31:50),"EAT"= c(51:76), "OCI"= c(77:94), "habit" = c(95:96))

#my_communities = c(rep(1,30), rep(2,20), rep(3,26), rep(4,18),rep(5,2)) 

#myplot <- plot(mynetwork.sympt, layout = "spring", groups = my_groups, labels=new_names)

#mybridge <- bridge(myplot, communities= my_communities, useCommunities = "all", directed = NULL, nodes = NULL)

#plot(mybridge, include = "Bridge Strength")

#plot(mybridge, include = "Bridge Expected Influence (1-step)")
```

Compute the bridge stability -- not reported in the main manuscript

```{r brige_stability,echo=TRUE, message= FALSE, warning= FALSE}
#caseDroppingboot <- bootnet(mynetwork.sympt, boots=1000, nCores = 4, type = "case", statistics=c("bridgeStrength", "BridgeExpectedInfluence"), communities=my_groups)

#corStability(caseDroppingboot)

#plot(caseDroppingboot,statistics = "bridgeStrength")
#plot(caseDroppingboot,statistics = "BridgeExpectedInfluence")

#nonParametricBoot <- bootnet(mynetwork.sympt, boots=1000, nCores = 4, type = "nonparametric", statistics=c("bridgeStrength", "BridgeExpectedInfluence"), communities=my_groups)


#plot(nonParametricBoot ,statistics = "bridgeStrength", plot = "difference")
#plot(nonParametricBoot ,statistics = "BridgeExpectedInfluence", plot = "difference")
```
